The value of intermediation

### 2022-09-14 src/presentation/presentation.qmd
Add manim figure about the timing of the game

::: {.column width="45%"}
 1. Firms decide whether to invest at cost $c$
 2. Platform entry fees and decisions are negotiated
 3. Firms and platforms set product prices
 4. Consumers choose products

**Idea:** 2. stage bargaining is over *final allocations*
:::

>>>>

::: {.column width="45%"}
::: {.fragment .fade-in fragment-index=2}
 1. Firms decide whether to invest at cost $c$
:::
::: {.fragment .fade-in fragment-index=3}
 2. Platform entry fees and decisions are negotiated
:::
::: {.fragment .fade-in fragment-index=4}
 3. Firms and platform set product prices, consumers buy products
:::

::: {.fragment .fade-in fragment-index=6}
**Idea:** 2. stage bargaining is over *final allocations*
:::
:::

::: {.column width="55%"}
::: {.r-stack}

::: {.fragment fragment-index=1}
<video data-autoplay src="../../out/manim_figures/videos/market_structure/800p60/sections/draw_objects.mp4" />
:::
::: {.fragment fragment-index=2}
<video data-autoplay src="../../out/manim_figures/videos/market_structure/800p60/sections/investment.mp4" />
:::
::: {.fragment fragment-index=3}
<video data-autoplay src="../../out/manim_figures/videos/market_structure/800p60/sections/platform_entry.mp4" />
:::
::: {.fragment fragment-index=4}
<video data-autoplay src="../../out/manim_figures/videos/market_structure/800p60/sections/pricing_game.mp4" />
:::
::: {.fragment fragment-index=5}
<video data-autoplay src="../../out/manim_figures/videos/market_structure/800p60/sections/everyone_enters.mp4" />
:::
::: {.fragment fragment-index=6}
<video data-autoplay src="../../out/manim_figures/videos/market_structure/800p60/sections/shapley_values.mp4" />
:::
